Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-22 alloscore_manuscript/alloscore-application-shorter.Rnw
some progress on short supp
add Acknowledgements

To make this a more easily interpreted measure of forecast performance, we will adjust the raw score by subtracting the minimum loss
achievable by an \emph{oracle} allocator which has precise foreknowledge of the outcomes $y_i$.
When the oracle has sufficient resources to meet the total need, i.e., when $\sum_{i=1}^{N}y_i \leq K$, the oracle's loss is zero 
and allocation score coincides with the raw score.
On the other hand, when the oracle cannot cover all need and incurs a loss of $L \cdot \left(\sum_{i=1}^{N}y_i - K \right) > 0$, we adjust
the raw score by this loss.
The oracle-adjusted score can therefore be written as
\begin{align}
S_A(F, y; K)  &= S_A^{\text{raw}}(F, y; K) - L \cdot \max\left(0,\sum_{i=1}^{N}y_i - K\right) \\
&= L\left\{\sum_{i=1}^N \max(0, y_i - x_i^{F,K}) -  \max\left(0,\sum_{i=1}^{N}y_i - K\right)\right\}
\end{align}
The oracle adjustment aligns with a common theme in economic decision theory that \emph{opportunity loss} (often known as \emph{regret} or (negative) \emph{relative utility}) is often a more important quantity than absolute loss (see e.g., \cite{DIECIDUE201788}).

@@

>>>>

To make this a more easily interpreted measure of forecast performance, we will adjust the raw score by subtracting the minimum loss
achievable by an \emph{oracle} allocator which has precise foreknowledge of the outcomes $y_i$.
When the oracle has sufficient resources to meet the total need, i.e., when $\sum_{i=1}^{N}y_i \leq K$, the oracle's loss is zero 
and allocation score coincides with the raw score.
On the other hand, when the oracle cannot cover all need and incurs a loss of $L \cdot \left(\sum_{i=1}^{N}y_i - K \right) > 0$, we adjust
the raw score by this loss.
The oracle-adjusted score can therefore be written as
\begin{align}
S_A(F, y; K)  &= S_A^{\text{raw}}(F, y; K) - L \cdot \max\left(0,\sum_{i=1}^{N}y_i - K\right) \\
&= L\left\{\sum_{i=1}^N \max(0, y_i - x_i^{F,K}) -  \max\left(0,\sum_{i=1}^{N}y_i - K\right)\right\}.
\end{align}
The oracle adjustment aligns with a common theme in economic decision theory that \emph{opportunity loss} (often known as \emph{regret} or (negative) \emph{relative utility}) is often a more important quantity than absolute loss (see e.g., \cite{DIECIDUE201788}).

@@

\section*{Acknowledgements}
This work has been supported by the National Institutes of General Medical Sciences (R35GM119582) and the U.S. CDC(1U01IP001122). The content is solely the responsibility of the authors and does not necessarily represent the official views of NIGMS, the National Institutes of Health, or CDC.
